Case study: Genome-Wide Association Analyses (GWAS)

### 2018-03-27 datasets/GWAS/GWAS.Rmd
Fix variable typo in plotting call; remove SLURM command in submit script

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$effect_size <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateLinePlot(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 trans = "log1p")
covariateLinePlot(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25)
```

>>>>

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$effect_size <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateLinePlot(sbAF, alpha=0.05, covname="effect_size", nbins=25, 
                 trans = "log1p")
covariateLinePlot(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25)
```
